---
title: "task2"
author: "Keyu Mao"
date: "2023/6/8"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the task, we will build a model of propensity scores using logisitic regression.

```{r}
data <- read.csv("final_data.csv")
head(data)
```


```{r}
library(MatchIt)
library(ggplot2)
ps_formula <- CO.AQI.Category~Ozone.AQI.Category+NO2.AQI.Category+Country
ps_model <- matchit(ps_formula, data = data, method = "nearest")
ps_scores <- ps_model$distance
data$propensity_score <- ps_scores
# Subset data for treatment and control groups
treatment_data <- data[data$CO.AQI.Category == 1, ]
control_data <- data[data$CO.AQI.Category == 0, ]

# Create density plots for propensity scores
ggplot() +
  geom_density(data = treatment_data, aes(x = propensity_score, fill = "Treatment"), alpha = 0.5) +
  geom_density(data = control_data, aes(x = propensity_score, fill = "Control"), alpha = 0.5) +
  labs(x = "Propensity Score", y = "Density", fill = "Group") +
  scale_fill_manual(values = c("blue", "red")) +
  theme_minimal()
```

### 2.3
In this task we will try to do matching. We can use package matchit and use propensity scores which are gained in the last section.


```{r}
match.method = matchit(CO.AQI.Category~propensity_score, data=data, method="nearest",ratio = 1)
match_data = match.data(match.method)
```

```{r}
summary(match.method, un = FALSE)
```

We may take a look at the smd of each covariate.

```{r}
smd <- function(variate, match_data.=match_data){
  ind_treat = which(match_data.$CO.AQI.Category == 1)
  ind_control = which(match_data.$CO.AQI.Category == 0)
  treat = data[[variate]][ind_treat]
  control = data[[variate]][ind_control]
  smd = abs(mean(treat)-mean(control))/sqrt((var(treat)+var(control))/2)
  smd
}
cat(c("The smd of Ozone.AQI.Category:", smd('Ozone.AQI.Category')))
cat(c("\nThe smd of NO2.AQI.Category:", smd('NO2.AQI.Category')))
cat(c("\nThe smd of Country:", smd('Country')))
```


As we can see in the above results, the smd of each covariate is fewer than 0.1. Indicating that the covariate balance has to some degree been achieved.

Then we can compute ATT

```{r}
att <- function(match_data){
  ind_treat = which(match_data$CO.AQI.Category == 1)
  ind_control = which(match_data$CO.AQI.Category == 0)
  treat = match_data$PM2.5.AQI.Value[ind_treat]
  control = match_data$PM2.5.AQI.Value[ind_control]
  mean(treat)-mean(control)
}

cat("The att of matched data is:", att(match_data))
att_v = att(match_data)
```


Then we can compute ATC similarly.

```{r}
new_data = data
new_data$CO.AQI.Category = 1 - data$CO.AQI.Category
match.method = matchit(CO.AQI.Category~propensity_score, data=new_data, method="nearest",ratio = 1)
match_data = match.data(match.method)

cat(c("The smd of Ozone.AQI.Category:", smd('Ozone.AQI.Category')))
cat(c("\nThe smd of NO2.AQI.Category:", smd('NO2.AQI.Category')))
cat(c("\nThe smd of Country:", smd('Country')))
```

```{r}
summary(match.method)
```

We can see that all the smd of all covariates are lower than 0.1.

```{r}
atc <- function(match_data){
  ind_treat = which(match_data$CO.AQI.Category == 0)
  ind_control = which(match_data$CO.AQI.Category == 1)
  treat = match_data$PM2.5.AQI.Value[ind_treat]
  control = match_data$PM2.5.AQI.Value[ind_control]
  mean(treat)-mean(control)
}
cat("The atc of matched data is:", atc(match_data))
atc_v = atc(match_data)
```
Then we can compute ATE:

```{r}
prob = mean(data$CO.AQI.Category)
ATE = prob*att_v+(1-prob)*atc_v
cat("ATE is:", ATE)
```

### 2.4
In this task we will using weighting to reweigh our samples.

```{r}
data$weights <- ifelse(data$CO.AQI.Category==1, 1/data$propensity_score, 1/(1-data$propensity_score))

E_Y_1 <- sum(data$PM2.5.AQI.Value*data$weights*data$CO.AQI.Category)/sum(data$weights*data$CO.AQI.Category)

E_Y_0 <- sum(data$PM2.5.AQI.Value*data$weights*(1-data$CO.AQI.Category))/sum(data$weights*(1-data$CO.AQI.Category))

cat("The ACE computed under weighted is:", E_Y_1-E_Y_0)
```

### 

```{r}
# Example propensity score model using stratification
model.stra <- matchit(ps_formula, data = data, method = "subclass")
data$weights<-NULL
matched_data <- match.data(model.stra)
strata <- unique(matched_data$subclass)
ace <- NULL  

for (i in 1:length(strata)) {
  stratum <- strata[i]
  
  treatment_group <- matched_data[matched_data$subclass == stratum & matched_data$CO.AQI.Category == 1, ]
  control_group <- matched_data[matched_data$subclass == stratum & matched_data$CO.AQI.Category == 0, ]
  
  mean_treatment <- mean(treatment_group$PM2.5.AQI.Value)
  mean_control <- mean(control_group$PM2.5.AQI.Value)
  
  ace[i] <- mean_treatment - mean_control
}
weighted_ace <- weighted.mean(ace, weights =table(matched_data$subclass))
weighted_ace
```
